MP MetaAnalysis

### 2018-11-11 Paper_Analyses.Rmd
Comments introduction

Acquiring a first language means that young learners are solving a host of tasks in a short amount of time. As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words. Before children can correctly pronounce a word, they already show evidence of sensitivity to slight variations in the phonological form of that word. This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words and are sensitive to changes that might signal a change in word meaning. As infants continue to develop into expert language users, their language processing matures and becomes more efficient. In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in their native language (e.g. cat-hat). In this paper, we aggregate and analyze the almost 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover its characteristics and the trajectory of its development.

  At the turn of the millenia, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997). Furthermore, when presented with familiar image pairs, children fixate on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998). Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English were presented with pairs of images (e.g. baby, dog) and their eye movements to each image were coded offline. On "correct" trials, children heard the correct label for one of the images (e.g. baby). On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g. vaby). Mean proportion of fixation to the target image (here: a baby) was calculated for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL). Mean fixations in correct trials were significantly greater than in mispronounced trials, although looks to the target were significantly greater than chance in both types of trials. We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance as *recognition*. Swingley and Aslin (2000) concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.

  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary concepts in early phonological development: *phonological constancy* and *phonological distinctiveness*. Phonological constancy is the ability to accept phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word. For example, different speakers - particularly across genders and accents - produce the same word with notable acoustic variation, although the word remains the same. In contrast, phonological distinctiveness describes the ability to differentiate between different words that happen to be phonologically similar, such as bad/bed or cat/hat. To successfully recognize words, infants must therefore simultaneously use both phonological constancy and distinctiveness to determine where phonological variation is appropriate and where it changes a word's meaning.

  In the current study, we focus on infants' developing ability to correctly apply the principles of phonological distinctiveness and constancy by using a meta-analytic approach to investigate mispronunciation sensitivity. Considering that infants are sensitive to mispronunciations and that, in general, their processing matures with development, we examine the shape of mispronunciation sensitivity over the course of the second and third year. There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively predicted by theoretical accounts and supported by single studies. By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants. Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

  Young infants may begin cautiously in their approach to word recognition, rejecting any phonological variation in familiar words and only later learning to accept appropriate variability. According to the Perceptual Attunement account, this describes a shift away from specific native phonetic patterns to a more mature understanding of the abstract phonological structure of words (Best 1994, 1995). This shift is predicted to coincide with the vocabulary spurt around 18 months, and is therefore related to vocabulary growth. In this case, we would expect the size of mispronunciation sensitivity to be larger at younger ages and *decrease* as the child matures and learn more words, although children continue to detect mispronunciations.
Indeed, young infants are less likely than older infants to demonstrate recognition of familiar words (Best, Tyler, Gooding, Orlando, & Quann, 2009; Mulak, Best, & Tyler, 2013) or learn new words (Schmale, Hollich, & Seidl, 2011) from accented speakers.

@@

Finally, some studies have found no difference in mispronunciation sensitivity at different ages. Swingley and Aslin (2000) tested infants over a wide age range of 5 months (18 to 23 months).  They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation effect) did not. This suggests that as children develop, they are more likely to look at the target in the presence of a mispronounced label and that age is not related to mispronunciation sensitivity. A similar response pattern has been found for British English learning infants aged between 18 and 24 months (Bailey & Plunkett, 2002) as well as younger French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, & Frauenfelder, 2012). These studies award support to the prediction that mispronunciation sensitivity does not change with development.

@@

  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship (Swingley & Aslin 2000; 2002; Bailey & Plunkett, 2002; Zesiger, Lozeron, Levy, & Frauenfelder, 2012; Swingley, 2009; Ballem & Plunkett, 2005; Mani & Plunkett, 2007; Mani, Coleman, & Plunkett, 2008). One notable exception comes from Mani and Plunkett (2010: keps and tups). Here, 12-month-old infants were divided into a low vocabulary and high vocabulary group based group median vocabulary size. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations. Taken together, although receiving considerable support from theories of phono-lexical processing in language acquisition, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity. In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to further disentangle the disconnect between theory and experimental results.

Taken together, the studies we have reviewed begin to paint a picture of the development of mispronunciation sensitivity. Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding. Meta-analyses can not only help us summarize the current state of research, but can also help us evaluate theories to drive future research and make hands-on recommendations for experiment planning.

>>>>

Acquiring a first language means that young learners are solving a host of tasks in a short amount of time. As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words [Primir, Kuhl, Best]. In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in their native language (e.g. cat-hat). To build robust language knowledge, it seems ueful to acquire this ability early during development. Indeed, before children can correctly pronounce a word, they already are aware that slight phonological deviations might signal a change in word meaning []. This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words. As infants continue to develop into expert language users, their language processing matures and becomes more efficient, including their knowledge of what consistutes a permissible versus word-changing phonological deviation. In this paper, we aggregate and analyze the almost 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover its characteristics and the trajectory of its development.

  At the turn of the millenia, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997). Furthermore, when presented with familiar image pairs, children fixate on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998; Tincoff & Jusczyk, 1999). Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g. a baby and a dog) and their eye movements to each image were recorded and subsequently coded offline. On "correct" trials, children heard the correct label for one of the images (e.g. "baby"). On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g. "vaby"). The mean proportion of fixations to the target image (here: a baby) was calculated separately for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL). Mean fixations in correct trials were significantly greater than in mispronounced trials, and in both conditions looks to the target were significantly greater than chance. We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance in each condition as *recognition*. Swingley and Aslin (2000) concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.

[Christina: changed concepts to mechanisms in the next paragraph, because I want to refer to what they represent, but I am not sure it\s the right term]

  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary mechanisms in early phonological development: *phonological constancy* and *phonological distinctiveness*, which are both present in the mature language processing system. Phonological constancy is the ability to resolve phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word. For example, different speakers - particularly across genders and accents - produce the same word with notable acoustic variation, although the word remains the same. In contrast, phonological distinctiveness describes the ability to differentiate between different words that happen to be phonologically similar, such as bad/bed or cat/hat. To successfully recognize words, speakers of a given language must therefore simultaneously use both phonological constancy and distinctiveness to determine where phonological variation is appropriate and where it changes a word's meaning. Both abilities have to be acquired, because language systems differ in which sounds signal a meaning change.

  In the current study, we focus on infants' developing ability to correctly apply the principles of phonological distinctiveness and constancy by using a meta-analytic approach to investigate mispronunciation sensitivity. Considering that infants are sensitive to mispronunciations and that, in general, their processing matures with development, we examine the shape of mispronunciation sensitivity over the course of the second and third year. There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively predicted by theoretical accounts and supported by single studies. By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see Frank et al., 2018; for a notable exception). Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

  Young infants may begin cautiously in their approach to word recognition, rejecting any phonological variation in familiar words and only later learning to accept appropriate variability. According to the Perceptual Attunement account, this describes a shift away from specific native phonetic patterns to a more mature understanding of the abstract phonological structure of words (Best 1994, 1995). This shift is predicted to coincide with the vocabulary spurt around 18 months, and is therefore related to vocabulary growth. In this case, we would expect the size of mispronunciation sensitivity to be larger at younger ages and *decrease* as the child matures and learn more words, although children continue to detect mispronunciations.
Indeed, young infants are more perturbed by accented speakers than older infants in their recognition of familiar words (Best, Tyler, Gooding, Orlando, & Quann, 2009; Mulak, Best, & Tyler, 2013) or learning of new words (Schmale, Hollich, & Seidl, 2011).

@@

Finally, some studies have found no difference in mispronunciation sensitivity at different ages. Swingley and Aslin (2000) tested infants over a wide age range of 5 months (18 to 23 months).  They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation sensitivity) did not. This suggests that as children develop, they are more likely to look at the target in the presence of a mispronounced label and that age is not related to mispronunciation sensitivity. A similar response pattern has been found for British English learning infants aged between 18 and 24 months (Bailey & Plunkett, 2002) as well as younger French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, & Frauenfelder, 2012). These studies award support to the prediction that mispronunciation sensitivity does not change with development.

@@

  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship (Swingley & Aslin 2000; 2002; Bailey & Plunkett, 2002; Zesiger, Lozeron, Levy, & Frauenfelder, 2012; Swingley, 2009; Ballem & Plunkett, 2005; Mani & Plunkett, 2007; Mani, Coleman, & Plunkett, 2008). One notable exception comes from Mani and Plunkett (2010: keps and tups). Here, 12-month-old infants were divided into a low and high vocabulary group based on median vocabulary size. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations. Taken together, although receiving considerable support from theories of phono-lexical processing in language acquisition, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity. In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to further disentangle the disconnect between theory and experimental results.

In sum, the studies we have reviewed begin to paint a picture of the development of mispronunciation sensitivity. Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of early language development. Meta-analyses can provide thus further insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and their mispronunciations sensitivity. Because we aggregate data over various age groups, this meta-analysis can also investigate the role of maturation by assessing the impact of age and vocabulary size. 
As a consequence, our results will be important in evaluating theories and drive future research. We also make hands-on recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses (Bergmann et al., 2018).
